Pillar 1 - Sequential Pattern Mining

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
minor changes
removes unnecessary

  AR %>%
    as("data.frame") %>%
    filter(
      count >= 1
    ) %>%
    mutate(
      rules = str_remove_all(rules, pattern = "[{]"),
      rules = str_remove_all(rules, pattern = "[}]"),
      # rules = str_remove(rules, pattern = "[{]"),
      # rules = str_remove(rules, pattern = "[}]"), #this is needed 4 times, because it only removes the first instance
      `rhs.support` = confidence / lift
    ) %>%
    separate(rules, into = c("lhs", "rhs"), sep="=>") %>%
    mutate_at(
      c("support", "lhs.support", "confidence", "rhs.support", "lift"),
      funs(round(., 5))
    ) %>%
    select(
      lhs, rhs,
      support, count, lhs.support,
      confidence, rhs.support,
      lift
    ) %>%
    arrange(
      desc(count)
    )

>>>>

  AR %>%
    as("data.frame") %>%
    filter(
      count >= 1
    ) %>%
    mutate(
      rules = str_remove_all(rules, pattern = "[{]"),
      rules = str_remove_all(rules, pattern = "[}]"),
      `rhs.support` = confidence / lift
    ) %>%
    separate(rules, into = c("lhs", "rhs"), sep="=>") %>%
    mutate_at(
      c("support", "lhs.support", "confidence", "rhs.support", "lift"),
      funs(round(., 5))
    ) %>%
    select(
      lhs, rhs,
      support, count, lhs.support,
      confidence, rhs.support,
      lift
    ) %>%
    arrange(
      desc(count)
    )
